### 2020-07-16 paper.tex
tweak intro

The contributions of this paper include:
\begin{enumerate}
\item A measure-theoretic formulation of involutive MCMC on general state spaces.
\item A mathematical formulation of state spaces consisting of arbitrary key-value stores (i.e. dictionaries) that formalizes the space of execution traces of Gen probabilistic programs, and a formulation of involutive MCMC on these spaces.
\item A differentiable programming language for defining bijections between spaces of traces of probabilistic programs.
\item An algorithm that automates the implementation of an involutive MCMC kernel given two probabilistic programs and a differentiable program encoding the involution, using automatic differentiation and tracing of probabilistic programs.
\item An extension to the algorithm that exploits sparsity in the involution to reduce the computational complexity of an involutive MCMC kernel from $O(N^2)$ to $O(1)$ in common cases.
\item An algorithm that dynamically detects errors in the specification of an involutive MCMC kernel.
\end{enumerate}

>>>>

The contributions of this paper include:
\begin{enumerate}
\item A measure-theoretic formulation of involutive MCMC on general state spaces.
\item A mathematical formulation of state spaces consisting of arbitrary key-value stores (i.e. dictionaries) that formalizes the space of execution traces of Gen probabilistic programs, and a formulation of involutive MCMC on these spaces.
\item A differentiable programming language for defining bijections between spaces of traces of probabilistic programs.
\item An algorithm that automates the implementation of an involutive MCMC kernel given two probabilistic programs and a differentiable program encoding the involution, using automatic differentiation and tracing of probabilistic programs.
\item An extension to the algorithm that exploits sparsity in the involution to reduce the computational complexity of an involutive MCMC kernel from $O(N^2)$ to $O(1)$ in common cases where $N$ is the dimensionality of the latent space.
\item An algorithm that dynamically detects errors in the specification of an involutive MCMC kernel.
\end{enumerate}
